Distance Sampling in \proglang{R}

### 2017-11-14 paper.Rnw
remove K-S tests from paper

Q-Q plots can be inspected visually, though this is prone to subjective judgments. Therefore, we also quantify the Q-Q plot's information using a Kolmogorov-Smirnov or Cram\'{e}r-von Mises test \citep{Burnham:2004vd}. Both test whether points from the EDF and CDF are from the same distribution. The Kolmogorov-Smirnov uses the test statistic of the largest difference between a point on the Q-Q plot and the line $y=x$, whereas the Cram\'{e}r-von Mises test uses the sum of all the differences. As it takes into account more information and is therefore more powerful, the Cram\'{e}r-von Mises is generally preferred. A significant result from either test gives evidence against the null hypothesis (that the data arose from the fitted model), suggesting that the model does not fit the data well.

@@

The authors would like to thank the many users of \pkg{Distance}, \pkg{mrds} and Distance for Windows who have contributed bug reports and suggestions for improvements over the years. We would particularly like to thank Steve Buckland, David Borchers, Tiago Marques, Jon Bishop and Lorenzo Milazzo for their contributions. We thank Tiago Marques a second time for helpful comments on an early version of the paper and Colin Beale who suggested the ``flatfile'' data format. We also thank Ken Burnham and David Anderson for fundamental contributions to the early development of these methods.

>>>>

Q-Q plots can be inspected visually, though this is prone to subjective judgments. Therefore, we also quantify the Q-Q plot's information using a Cram\'{e}r-von Mises test \citep{Burnham:2004vd} to test whether points from the EDF and CDF are from the same distribution. The Cram\'{e}r-von Mises test uses the sum of all the distances between a point on the Q-Q plot and the line $y=x$ to form a test statistic. As it takes into account more information and is therefore more powerful, the Cram\'{e}r-von Mises is generally more powerful than the Kolmogorov-Smirnov test, which uses the largest difference between a point on the Q-Q plot and the line $y=x$ (which is also available in \pkg{Distance}, though is not produced by default as it requires computationally demanding bootstraps). A significant result from either test gives evidence against the null hypothesis (that the data arose from the fitted model), suggesting that the model does not fit the data well.

@@

The authors thank the two anonymous reviewers for their constructive comments, which have greatly improved the paper and package. The authors would like to thank the many users of \pkg{Distance}, \pkg{mrds} and Distance for Windows who have contributed bug reports and suggestions for improvements over the years. We would particularly like to thank Steve Buckland, David Borchers, Tiago Marques, Jon Bishop and Lorenzo Milazzo for their contributions. We thank Tiago Marques a second time for helpful comments on an early version of the paper and Colin Beale who suggested the ``flatfile'' data format. We also thank Ken Burnham and David Anderson for fundamental contributions to the early development of these methods.
